\textbf{ Interpretable Gaussian Processes for Stellar Variability\\ I: Static Surfaces }

### 2020-12-25 tex/ms.tex
momre figs

>>>>

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/stability.pdf}
        \oscaption{stability}{%
            Log of the condition number of the covariance in the
            spherical harmonic basis, $\pmb{\Sigma}_{\mathbf{y}}$,
            as a function of the spherical harmonic degree of the
            expansion, $l_\mathrm{max}$. Different lines correspond
            to different values of $\pmb{\theta}_\bullet$ drawn
            from a uniform prior (see text for details).
            In the majority of the cases, the matrix becomes ill-conditioned
            above $l_\mathrm{max} = 15$.
            \label{fig:stability}
        }
    \end{centering}
\end{figure}

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Speed tests \xxx{(TODO)}.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}
